%!TEX root = main.tex

\chapter*{Resource attribution}

The following is a list of the sources of all models, textures, and other assets downloaded from the web to use in this project.

\section*{3D models}

\href{https://www.models-resource.com/3ds/personaqshadowofthelabyrinth/model/14509/}{Makoto} (player character), \href{https://www.models-resource.com/3ds/personaqshadowofthelabyrinth/model/14582/}{Samurai} (common enemy), \href{https://www.models-resource.com/3ds/personaqshadowofthelabyrinth/model/14564/}{Phantom Master} (boss enemy): provided by the Video Games Resource community. We removed some unnecessary elements.

Projectile for the Samurai's special attack: designed in Blender by us.

Cube of Babylon: our 3D reproduction of the current logo of BabylonJS.

All other non-primitive 3D models: original Blender files by the user Quaternius on the OpenGameArt forum: \href{https://opengameart.org/content/lowpoly-modular-dungeon-pack}{Modular Dungeon}, \href{https://opengameart.org/content/low-poly-rpg-pack}{Items}. UV mappings and some very minor adaptations by us.

\section*{Other}

Textures for Makoto, Samurai, Phantom Master: color textures provided along with the models. Other textures realized by us via simple editing of the color ones in GIMP.

Fireball emissive texture: a map of the Sun shot by the NASA STEREO probes in 2012. We could not find an official NASA source, possibly because of the age of the image, but this article (in Italian) explains its origin: \url{https://www.rivistageomedia.it/201210287530/Archivio/studio-del-sole-3d-dalle-sonde-stereo-della-nasa}

\href{https://www.textures-resource.com/nintendo_switch/mariokart8deluxe/texture/14725/}{Sky maps}: provided by the Video Game Resource community.

All other textures: \href{http://www.texturise.club/}{texturise.club}, whether taken directly or by combination of two or more textures from there.

All particles: \href{https://doc.babylonjs.com/toolsAndResources/assetLibraries/availableTextures}{BabylonJS Texture Library}.

Icons in the battle UI: The \href{https://opengameart.org/content/ui-pack-space-extension}{Charge State icon} is by the user Kenney on the OpenGameArt forum. The rest are from \href{https://game-icons.net/}{game-icons.net} and \href{https://iconmonstr.com/}{iconmonstr.com}, colored and slightly edited by us in Inkscape.